Relationship Between Common Stream Health Indicators

### 2021-12-13 products/manuscript/Manuscript.Rmd
Manuscript Edits - CC

Stream health and water quality are typically measured by a stream's physical characteristics (chemistry, surrounding land use area, channelization, etc.); microbial impacts(fecal indicator), and ecology (diversity of indicator macroinvertebrates). However, these categories are usually analyzed separately to assess stream health. If the impact of urbanization on freshwater bodies is not uniform, environmental managers could be spending a lot of time and effort on monitoring programs that are not effective. Studies have shown conflicting results on what variables like conductivity, turbidity, e. coli cfu (fecal coliform indicator), nutrient (nitrogen and phosphorus) concentration, and biodiversity indicator score actually say about water quality. Therefore, a study was conducted assess how well all these parameters correlated with each other in the context of the Adopt-a-Stream method. Specifically, can you use one of the indicators mentioned (physical, microbial, and ecological) to describe the others to make a statement about overall stream health?

>>>>

Stream health and water quality are typically measured by a stream's physical characteristics (chemistry, surrounding land use area, channelization, etc.); microbial impacts(fecal indicator), and ecology (diversity of indicator macroinvertebrates). However, these categories are usually analyzed separately to assess stream health. If the impact of urbanization on freshwater bodies is not uniform, environmental managers could be spending a lot of time and effort on monitoring programs that are not effective. Studies have shown inconsistent results on what variables like conductivity, turbidity, e. coli cfu (fecal coliform indicator), nutrient (nitrogen and phosphorus) concentration, and biodiversity indicator score actually say about water quality. Therefore, this study was conducted assess how well all these parameters correlated with each other in the context of the Adopt-a-Stream method. Specifically, can you use one of the indicators mentioned (physical, microbial, and ecological) to describe the others to make a statement about overall stream health?
